**The status of the microbial census: an update**

### 2015-12-01 Schloss_Census2_mBio_2015.Rmd
Generate Venn diagram data for OTU overlap between methods

###### here #######

@@

grepl("^[^\\.]*$", rownames(bact))

dim(bact[bact$publication_doi=="10.1038/nature12352" & !is.na(bact$publication_doi),])
#[1] 95 31

```
***New technologies to access novel biodiversity***
Assembly of metagenomic and single cell shotgun sequence data offers the hope of identifying large fragments of genomic data from as yet uncultured organisms. To test the ability of single cell technologies to identify

>>>>

@@

***New technologies to access novel biodiversity***
Assembly of metagenomic and single cell shotgun sequence data offers the hope of identifying large fragments of genomic data from as yet uncultured organisms. To test the ability of single cell technologies to identify
